Refunctionalization of Abstract Abstract Machines

### 2018-08-20 paper/paper.tex
misc

CFA2 is the first solution that solves the return-flow problem~\cite{vardoulakis2010cfa2},
which is formulated as a monovariant analysis on programs written in continuation-passing style.
The original presentation of CFA2 has an exponential runtime complexity, 
and several improvements are proposed by \citet{vardoulakis-diss12} afterwards.
But implementing CFA2 is considered requiring significant engineering efforts.

>>>>

CFA2 is the first solution that solves the return-flow problem~\cite{vardoulakis2010cfa2},
which is formulated as a monovariant analysis on programs written in continuation-passing style.
The original presentation of CFA2 has an exponential runtime complexity, 
and several variants and improvements are proposed by \citet{vardoulakis-diss12} afterwards.
But implementing CFA2 is considered requiring significant engineering efforts.
